Explore spatial allocation

### 2021-02-22 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished distance to coast calcs. Fixed jersey bivalves so we aren't double counting

# read in shp
farms_all <- ASC_bivalve %>%
  cbind(iso)

@@

@@

farms_jey <- data.frame(lat = c(49.172680993306905, 49.220095937386375, 49.169912669200976, 49.242435452408536, 49.20656011166959),
                        lon = c(-2.0255193115109957, -2.0215887506551438, -2.0230904378277916, -2.060618920921559, -2.0158403231425996)) %>%
  mutate(iso3c = "JEY") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_jey, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_jey.csv"))

## visualize it 
farms_jey <-  st_as_sf(farms_jey, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_jey)

>>>>

# read in shp
farms_all <- ASC_bivalve %>%
  cbind(iso) %>%
  mutate(iso3c = ifelse(str_detect(comp_nm, "Jersey"), "JEY", iso3c))

@@

 - UPDATE: This is not necessary. These companies are represented in the ASC data, but listed under the UK. I will fix this, so that we aren't double counting these farms.

@@

# farms_jey <- data.frame(lat = c(49.172680993306905, 49.220095937386375, 49.169912669200976, 49.242435452408536, 49.20656011166959),
#                         lon = c(-2.0255193115109957, -2.0215887506551438, -2.0230904378277916, -2.060618920921559, -2.0158403231425996)) %>%
#   mutate(iso3c = "JEY") %>%
#   mutate(data_quality = 4) %>%
#   mutate(action_needed = "Land mask")
# 
# write_csv(farms_jey, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_jey.csv"))
# 
# ## visualize it 
# farms_jey <-  st_as_sf(farms_jey, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_jey)

### 2021-02-22 marine/explore_spatial_allocation.Rmd
finished distance to coast calcs. Fixed jersey bivalves so we aren't double counting

n_farms <- all_farms %>%
  group_by(iso3c, data_quality, group) %>%
  summarise(n_farms = n()) %>%
  ungroup() %>%
  group_by(iso3c) %>%
  mutate(avg_quality = mean(data_quality)) %>%
  ungroup()

>>>>

```{r}
n_farms <- all_farms %>%
  group_by(iso3c, data_quality, group) %>%
  summarise(n_farms = n()) %>%
  ungroup() %>%
  group_by(iso3c) %>%
  mutate(avg_quality = mean(data_quality)) %>%
  ungroup()
